FraCaS: Temporal Analysis

### 2020-09-30 paper2020/paper.tex
list todos

The semantics of tense and aspect has been a long standing issue in
the study of formal semantics since the early days of Montague Grammar
and a number of different ideas have been put forth on the table to
deal with them throughout the years. Recent proposals include the
works of the following authors:
\citet{dowty:2012,prior:2003,steedman_productions_2000,higginbotham:2009,fernando:2015}.
%
The
semantics of tense and aspect have been also considered in the study of
Natural Language Inference (NLI). The various datasets
for NLI that have been proposed by the years contain examples that
have some implicit or explicit reliance on inferences related to tense
and aspect. One of the early datasets used to test logical approaches,
the FraCaS test suite~\citep{cooper:1996} contains a whole section
dedicated to temporal and aspectual inference (section 7 of the dataset). This part
of the FraCaS test suite has been notoriously difficult to tackle. In
fact, so far, no computational system has been capable to deal with it: when
authors report accuracy over the FraCaS test suite they
skip this section.
%
In fact, they also often skip the anaphora and ellipsis sections, the
exception being the system presented by
\citet{bernardy_type-theoretical_2017,bernardy_wide-coverage_2019},
which include support for anaphora and ellipsis but still omit the
temporal section.
%
In this paper, we take up the challenge of providing a
computationally viable account of tense and aspect to deal with the
notoriously difficult section 7 of the FraCaS test suite. Our account is not meant
to be a theoretically extensive account of tense and aspect, but rather an
account that is driven by the need to cover the test suite in a way
that is general enough to capture the test suite examples, \emph{while still covering the rest of the FraCaS test suite}.
%
The account is evaluated on the entailment properties of various
temporal and aspectual examples, as given by the test suite. As such,
we are not getting into the discussion of how tense and aspect might
affect grammaticality or infelicitousness of various sentences.
We assume that the sentences of the FraCaS suite are syntactically and
semantically correct, and strive to produce accurate logical
representations given that assumption. We further assume that the
entailment annotations of various problems are valid, and we use those
to evaluate the correctness of the logical representations of
sentences.

>>>>

The semantics of tense and aspect has been a long standing issue in
the study of formal semantics since the early days of Montague Grammar
and a number of different ideas have been put forth on the table to
deal with them throughout the years. Recent proposals include the
works of the following authors:
\citet{dowty:2012,prior:2003,steedman_productions_2000,higginbotham:2009,fernando:2015}.
%
The
semantics of tense and aspect have been also considered in the study of
Natural Language Inference (NLI). The various datasets
for NLI that have been proposed by the years contain examples that
have some implicit or explicit reliance on inferences related to tense
and aspect. One of the early datasets used to test logical approaches,
the FraCaS test suite~\citep{cooper:1996} contains a whole section
dedicated to temporal and aspectual inference (section 7 of the dataset). This part
of the FraCaS test suite has been difficult to tackle. That is,
so far, no computational system has been capable to deal with it: when
authors report accuracy over the FraCaS test suite they
skip this section.
%
In fact, they also often skip the anaphora and ellipsis sections, the
exception being the system presented by
\citet{bernardy_type-theoretical_2017,bernardy_wide-coverage_2019},
which include support for anaphora and ellipsis but still omit the
temporal section.
%
In this paper, we take up the challenge of providing a
computationally viable account of tense and aspect to deal with the
notoriously difficult section 7 of the FraCaS test suite. Our account is not meant
to be a theoretically extensive account of tense and aspect, but rather an
account that is driven by the need to cover the test suite in a way
that is general enough to capture the test suite examples, \emph{while still covering the rest of the FraCaS test suite}.
%
The account is evaluated on the entailment properties of various
temporal and aspectual examples, as given by the test suite. As such,
we are not getting into the discussion of how tense and aspect might
affect grammaticality or infelicitousness of various sentences.
We assume that the sentences of the FraCaS suite are syntactically and
semantically correct, and strive to produce accurate logical
representations given that assumption. We further assume that the
entailment annotations of various problems are valid, and we use those
to evaluate the correctness of the logical representations of
sentences.
